Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-03-13 template.tex
final big update (with figures) before April/March APS 2025

 \documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{empheq}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator\erf{erf}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

@@

@@

-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}\left( 2\pi j e^{2 j x z_0 - z_0^2 \right)

@@

@@

>>>>

 \documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{empheq}
\usepackage{verbatim}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator\erf{erf}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

@@

Finally, the derivative of the Faddeeva function is $dw/dz = 2j/\sqrt{\pi} - 2 zw(z)$.  Substituting for $dw/dz$ gives the final result:
+ R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) \label{eq:Re_result}

@@

-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}\left( 2\pi j e^{2 j x z_1 - z_1^2} - 2G(z_1) e^{-x^2} \right)

@@

Notice that $2\pi j x z_1 = 2\pi j f_0 t - \gamma t$.  Evaluating the derivative and simplifying gives the final result:
\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:Im_result}
\item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:
r_a(t) * s_a(t) = \\
\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) + \\
R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2}(1+j\sqrt{\pi} z w(z)) + \\
j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \\
j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}
The units of the convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq.\ref{eq:final} has these units.  The first term is proportional to $R_0 \sigma_t s(t)$, and $s(t)$ has units of $E_0 \sigma_t$, so the unit product is $R_0 E_0\sigma_t^2$.  The units of the second term are $R_0 E_0\sigma_t^2$.  The third term has units of $E_0\sigma_t^2 r_a(t)$, and $r_a(t)$ has units of $R_0$, so the unit product is $R_0 E_0\sigma_t^2$.  The fourth term has units of $R_0 \sigma_t s(t)$, like the first term.  Thus, all units check.  To check the limits, the parameters $z$ and $z_1$ must be recalled.  Combining prior definitions, the results are
z &= \sqrt{2}\sigma_t \pi f_0 + j\left(\frac{\sigma_t\gamma}{\sqrt{2}} - x\right) \\
z_1 &= f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)
Recall that $\sigma_t = 1/(2\pi \sigma_f)$, and $x=t/(\sqrt{2}\sigma_t)$.  Substituting this into the definition of $z$ reveals that
z_1 = z + jx
Thus, when $t=0$, the two poles are equal, since $t=0$ means $x=0$.  Taking the magnitude of Eq. \ref{eq:final}, and multiplying by $1/2$, gives the final result:
\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) |
\item Two examples of comparisons of Eq. \ref{eq:final} to the convolution of $s(t)$ and $r(t)$ are given in Fig. \ref{fig:fig1} below.
\begin{figure}[hb]
\centering
\includegraphics[width=0.5\textwidth]{March12_plot1.pdf}
\includegraphics[width=0.5\textwidth]{March12_plot2.pdf}
\caption{\label{fig:fig1} (Top) The thin black line represents $s(t) * r(t)$.  The dark gray envelope represents the envelope of $s(t) * r(t)$ computed with the Python3 package scipy.special.hilbert. The light gray envelope represents Eq. \ref{eq:final}. (Bottom) Same as top, for different parameter values.}
\end{figure}

@@

\clearpage
